On the analytic structure of the linear response susceptibility in open systems

### 2018-03-08 AnalyticStructure_main.tex
Update on Overleaf.

The interesting aspect of equations \eqref{fluctuationStateEqMotion1} in the perspective of the present analysis is that they allow us to present a 
\emph{localization argument} for the fluctuation states. To clarify this statement we split the unperturbed Hamiltonian as the sum of the kinetic $\op T$ and potential 
$\op V$ term and solve \eqref{fluctuationStateEqMotion1} in the form of a self-consistent inhomogeneous Helmholtz equation by writing:
\be
\ket{f_p(\omega)} = \op G_H(\omega)\ket{s(\omega)} \;,
\ee
where we have introduced the Green function of the Helmholtz operator $\op G_H(\omega) = (k^2_p(\omega)-\op T)^{-1}$ with $k^2_p(\omega) = (\omega+\eps_p)$,
and the \emph{source term} is given by:
\be
\ket{s(\omega)} =  \op V\ket{f_p(\omega)} + \op Q_0(\op V'(\omega) + \op \Phi(\omega))\ket{\psi_p} \;.\nn
\ee
For open boundary conditions in three dimensions, the kernel of $\op G_H(\omega)$ in the coordinate representation reads: 
% \be\lb{HelmholtzKernelDef1}
% \bra{\r}\op G_H(\omega)\ket{\r'} = \frac{1}{4\pi} \left\{ 
% \begin{matrix}
% \frac{e^{-2k_p(\omega)|\r-\r'|}}{|\r-\r'|} \;,\; {\textrm for} \; \omega \leq |\eps_p| \\ 
% \frac{e^{\ii k_p(\omega)|\r-\r'|}}{|\r-\r'|} \;,\; {\textrm for} \; \omega > |\eps_p|
% \end{matrix}
% \right. \;,
% \ee
\be\lb{HelmholtzKernelDef1}
G_H(\omega,\r) = \frac{1}{4\pi} \left\{ 
\begin{matrix}
\frac{e^{-2k_p(\omega)|\r|}}{|\r|} \;,\; {\textrm for} \; \omega \leq |\eps_p| \\ 
\frac{e^{2\ii k_p(\omega)|\r|}}{|\r|} \;,\; {\textrm for} \; \omega > |\eps_p|
\end{matrix}
\right. \;,
\ee
and the $\r$-representation of the fluctuation states $f_p(\omega,\r)$ is expressed through a convolution integral between the kernel \eqref{HelmholtzKernelDef1} and
$\brket{\r}{s(\omega)}$. An inspection of the structure of \eqref{HelmholtzKernelDef1} evidences that, for each value of $p$, there exist a threshold value $\omega = |\eps_p|$, 
which govern the localization properties of the corresponding fluctuation state. Indeed, for $\omega > |\eps_p|$,  $G_H(\omega,\r)$ behaves as a spherical wave and its
convolution with the source term always give raises to a $f_p(\omega,\r)$ delocalized in the whole accessible space. On the contrary, for values of $\omega$ below the threshold,
$G_H(\omega,\r)$ contains an exponential damping factor and the localization features of $f_p(\omega,\r)$ are determined by the spatial behavior of the source term.

>>>>

The interesting aspect of equations \eqref{fluctuationStateEqMotion1} in the perspective of the present analysis is that they allow us to present a 
\emph{localization argument} for the fluctuation states. To clarify this statement we split the unperturbed Hamiltonian as the sum of the kinetic $\op T$ and potential 
$\op V$ term and solve \eqref{fluctuationStateEqMotion1} in the form of a self-consistent inhomogeneous Helmholtz equation by writing:
\be
\ket{f_p(\omega)} = \op G_H(\omega+\epsilon_p)\ket{s(\omega)} \;,
\ee
where we have introduced the Green function of the Helmholtz operator $\op G_H(\omega) = (\omega-\op T)^{-1}$, % with $k^2_p(\omega) = (\omega+\eps_p)$,
and the \emph{source term} is given by:
\be
\ket{s(\omega)} =  \op V\ket{f_p(\omega)} + \op Q_0(\op V'(\omega) + \op \Phi(\omega))\ket{\psi_p} \;.\nn
\ee
For open boundary conditions in three dimensions, the kernel of $\op G_H(\omega)$ in the coordinate representation reads: 
% \be\lb{HelmholtzKernelDef1}
% \bra{\r}\op G_H(\omega)\ket{\r'} = \frac{1}{4\pi} \left\{ 
% \begin{matrix}
% \frac{e^{-2k_p(\omega)|\r-\r'|}}{|\r-\r'|} \;,\; {\textrm for} \; \omega \leq |\eps_p| \\ 
% \frac{e^{\ii k_p(\omega)|\r-\r'|}}{|\r-\r'|} \;,\; {\textrm for} \; \omega > |\eps_p|
% \end{matrix}
% \right. \;,
% \ee
\be\lb{HelmholtzKernelDef1}
\bra{\r'} \op G_H(k^2) \ket\r = \frac{1}{4\pi} \begin{cases}
\frac{e^{-2k|\r - \r' |}}{|\r- \r' |} \;,\; & {\textrm for}\; k < 0\; \\ 
\frac{e^{2\ii k |\r-\r' |}}{|\r-\r' |} \;, & {\textrm for} \; k > 0
\end{cases}
\ee
%and the $\r$-representation of the fluctuation states $f_p(\omega,\r)$ is expressed through a convolution integral between the kernel \eqref{HelmholtzKernelDef1} and
%$\brket{\r}{s(\omega)}$.
An inspection of the structure of \eqref{HelmholtzKernelDef1} evidences that, for each value of $p$, there exist a threshold value $\omega = |\eps_p|$, 
which govern the localization properties of the corresponding fluctuation state. Indeed, for $\omega > |\eps_p|$,  $G_H(\omega,\r)$ behaves as a spherical wave and its
convolution with the source term always give raises to a $f_p(\omega,\r)$ delocalized in the whole accessible space. On the contrary, for values of $\omega$ below the threshold,
$G_H(\omega,\r)$ contains an exponential damping factor and the localization features of $f_p(\omega,\r)$ are determined by the spatial behavior of the source term.
